Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2023-02-10 Thesis/chapter/032-alt-theory-calculations.tex
finsh SVM base

\textbf{Support vector machines} 
\Gls{svm} are versatile machine learning algorithm first mentioned in 1992\cite{boser1992training}. 
\Gls{svm} is mainly used for classification, but can also be used for regression. 
Classifiction works by spanning a hyperplane between two categories in a way that the closest points from each category have the largest distance to the hyperplane. 
The distance from the points to the hyperplane is called margin.
These points are called support vectors and are used to define the hyperplane 
A \gls{svm} avoids overfitting by only using a subset - the support vectors - to fit the model. 
\td{The goal is to fit $w$ and $b$ such that the margin (the distance from the descission boundary is maximal.
As this the margin is inversely proportional to $\|w\|$, we aim to minimize $\|w\|$.
With the contraint that all data points are correctly classified $y_i(x_iw-b)\geqslant1$.}
In the same manner as no data points are found within the margin for classification, 
no data points should be found outside of the margin. 
If the data is not seperable by a hyperplane the kernel trick can be used. 
The downside of \gls{svm} is that it is very
\td{$\text{min}\frac{1}{N} \sum_{i=1}^{N} max(0,1- y_i(\mathbf{x}x_i-b)) + \lambda \|w\|$
The downside of \gls{svm} is that it is very sensitive to outliers.}

$\min_{w,b} \|w\|$

$ y_i(w \cdot x_i - b)\leqslant 1$

Summary of SVM from Cherkassky's \textit{Learning from Data}\cite{cherkassky1998learning}
The \gls{svm} was initially developed by V. Vapnik for the binary classification of seperable data, then improved to handle non-sperable data and eventually adapted to solve regression problems.
The concepts of \gls{svm} will be discussed in the same chronological order.

The decision boundary can be expressed as an hyperplane
\begin{equation}
	\hat{\mathbf{y}} = D(\mathbf{x}) = \mathbf{w} \cdot \mathbf{x} + w_0 
\end{equation}
with $
\mathbf{y} \in \lbrace +1, -1 \rbrace^n ,\,
\mathbf{w} \in \mathbb{R}^d ,\,
\mathbf{x} \in \mathbb{R}^{n \times d} 
$.
A hyperplane which separate the data will satisfy the following equation: 
\begin{equation}
	\label{eq:svm01}
	y_i(\mathbf{w} \cdot \mathbf{x}_i + w_0 ) \geqslant 1, \qquad i=1,\dots,n
\end{equation}
The distance from the decision boundary to the nearest points shall be denoted as $\tau$ and should be maximized. 
Inequality \ref{eq:svm01} is an equation for the support vectors. 
If we now take a vector from a positive support vector $x_+$ to a negative support vector $x_-$ and project it on to the unit vector of $w$ we get the width of the margin. 
\begin{equation}
	\label{eq:svm02}
\begin{aligned} 
	\text{width} &= (x_+ - x_-) \cdot \frac{w}{\|w\|} \\
		&= ( (1-b)/w - (-1-b)/w ) ) \cdot \frac{w}{\|w\|} \\
		&= \frac{2}{w} \cdot \frac{w}{\|w\|} = \frac{2}{\|w\|}
\end{aligned}
\end{equation}
\td{draw sketch and make \ref{eq:svm02} on two lines}

but before are the hyperplanes which go through the support vectors for positive sample: 
\begin{equation}
	y
\end{equation}

>>>>

\textbf{Support vector machines} 
\Gls{svm} are versatile machine learning algorithm first mentioned in 1992\cite{boser1992training}. 
%
The \gls{svm} was initially developed by V. Vapnik for the binary classification of seperable data, then improved to handle non-sperable data and eventually adapted to solve regression problems.
The concepts of \gls{svm} will be discussed in the same chronological order. 
%
%\Gls{svm} is mainly used for classification, but can also be used for regression. 
Classifiction works by spanning a hyperplane between two linearly separable categories in a way such that the closest points from each category have the largest distance to the hyperplane. 
The distance from the points to the hyperplane is called margin $\tau$.
These points are called support vectors and are used to define the hyperplane.
A \gls{svm} avoids overfitting by only using a subset - the support vectors - to fit the model. 
%Among the many advantages of \gls{svm} are the 
%convex loss function, avoidance of overfitting by only using a subset of input vectors (the support vectors) to fit the model.
The goal is to find the decision boundary which correctly classifies all samples with the biggest margin. 
%\td{The goal is to fit $w$ and $b$ such that the margin (the distance from the descission boundary is maximal.
%As this the margin is inversely proportional to $\|w\|$, we aim to minimize $\|w\|$.
%With the contraint that all data points are correctly classified $y_i(x_iw-b)\geqslant1$.}
%In the same manner as no data points are found within the margin for classification, 
%no data points should be found outside of the margin. 
%If the data is not seperable by a hyperplane the kernel trick can be used. 
%\td{$\text{min}\frac{1}{N} \sum_{i=1}^{N} max(0,1- y_i(\mathbf{x}x_i-b)) + \lambda \|w\|$
%The downside of \gls{svm} is that it is very sensitive to outliers.}
%
%$\min_{w,b} \|w\|$ 
%
%$ y_i(w \cdot x_i - b)\leqslant 1$ 
%
%Summary of SVM from Cherkassky's \textit{Learning from Data}\cite{cherkassky1998learning}
%The \gls{svm} was initially developed by V. Vapnik for the binary classification of seperable data, then improved to handle non-sperable data and eventually adapted to solve regression problems.
%The concepts of \gls{svm} will be discussed in the same chronological order. 
%
The decision boundary can be expressed as an hyperplane
\begin{equation}
	\hat{\mathbf{y}} = h(\mathbf{x}) = \mathbf{w} \cdot \mathbf{x} + b
\end{equation}
with $
\mathbf{y} \in \lbrace +1, -1 \rbrace^n ,\,
\hat{\mathbf{y}} \in \mathbb{R}^n ,\,
\mathbf{w} \in \mathbb{R}^d ,\,
\mathbf{x} \in \mathbb{R}^{n \times d} 
$.
The constraint of the positive and negative support vectors ($x^+$ and $x^-$, respectively) satisfying
\begin{align}
	\mathbf{w} \cdot x^+ + b &= 1 \\
	\mathbf{w} \cdot x^- + b &= -1 
\end{align}
can be generalized to 
%A hyperplane which separate the data will satisfy the following equation: 
\begin{equation}
	\label{eq:svm01}
	y_i(\mathbf{w} \cdot \mathbf{x}_i + b ) \geqslant 1 %\qquad i=1,\dots,n
\end{equation}
where $y_i$ being the labels of the training data. 
The width of the margin can be inferred by projecting the vector spanning between two support vectors 
on opposite sides of the decision boundary onto the unit vector perpendicular to the hyperplane. 
%The distance from the decision boundary to the nearest points shall be denoted as $\tau$ and should be maximized. 
%Inequality \ref{eq:svm01} is an equation for the support vectors. 
If we now take a vector from a positive support vector $x^+$ to a negative support vector $x^-$ and project it on to the unit vector of $w$ (which is perpendicular to the hyperplane), 
we get the width of the margin. 
\begin{equation}
	\label{eq:svm02}
	\begin{aligned} 
		2\tau &= (x^+ - x^-) \cdot \frac{\mathbf{w}}{\|\mathbf{w}\|} \\
			&= (x^+ \cdot \mathbf{w} - x^-\cdot \mathbf{w} ) \cdot \frac{1}{\|\mathbf{w}\|} \\
			&= ( (1-b) - (-1-b) ) \cdot \frac{1}{\|\mathbf{w}\|} \\
			&= \frac{2}{\|w\|}
	\end{aligned}
\end{equation}
%\td{draw sketch and make \ref{eq:svm02} on two lines}
Thus maximizing the margin is equivalent with minimizing $\|\mathbf{w}\|$. 
By incorporation the contraint (eq. \ref{eq:svm01}) via the Lagrangian multiplier method we arrive at the loss function: 
\begin{equation}
	\label{eq:svm03}
	\mathcal{L} = \frac{1}{2} \|\mathbf{w}\| - \sum_i^n \alpha_i [ y_i ( w_i \cdot x_i + b) -1 ] 
\end{equation}
which can be rewritten by some mathematical wizardry (setting the partial derivatives of the lagrangian 
$\frac{\partial \mathcal{L}}{\partial \mathbf{w}}$ and $\frac{\partial \mathcal{L}}{\partial b}$ to zero and inserting into eq. (\ref{eq:svm03})): 
\begin{equation}
	\mathcal{L} = \sum_i^n \alpha_i - \frac{1}{2} \sum_i^n \sum_i^n \alpha_i \alpha_j y_i y_j \mathbf{x}_i \cdot \mathbf{x}_j 
\end{equation}
\td{write about kernel trick and non strick}
